\begin{rubric}{Experience}
\entry*[2014 -- $\cdots$]%
	\textbf{Member}\, Minnesota Extensible Language Tools group, University of Minnesota--Twin Cities, Minneapolis, MN.
	\url{https://melt.cs.umn.edu}
	\par Lead developer of \silver{}, a programming language for modular compiler
	% and language tool
	implementation, based on attribute grammar and functional paradigms.
	Built related tooling, such as a language server/VS Code extension and Jenkins continuous integration.
	Invented new approach to context-aware syntax tree transformations, by integrating attribute grammars and strategic term rewriting.
	\par Primary maintainer for \ableC{}, an extensible C11 compiler frontend in \silver{}.
	Developed extensions to C adding algebraic data types/pattern matching, Prolog-style relations and queries,
	term rewriting, closures, Halide-inspired specification of optimizing transformations on loops, C++-style templates and operator overloading.
%
\entry*[2021 -- 2023]%
	\textbf{AI Resident}\, X, the moonshot factory / Labs @ Google, Mountain View, CA.
	\par Member of the Codey team, focused on using AI to assist developers using large language models tailored for coding tasks.
	Researched bulk synthesis of code translation and transformation datasets using \silver{}.
	Filed 2 pending patent applications.
%
\entry*[2021]%
	\textbf{Software Engineering Ph.D Intern}\, Google, Remote.
	\par Developed a more flexible means of specifying optimization passes in the TensorFlow compiler back-end using Haskell.
%
\entry*[2020 -- 2021]%
	\textbf{Ph.D Student Researcher}\, Google, Remote.
	\par Development on the compiler for Bluespec, an open-source high-level hardware synthesis language.
	Contributed generic programming features based on GHC.Generics, allowing for the removal of large amounts of boilerplate.
	%Implemented several long-standing feature requests, improving consistency in language semantics.
%
\entry*[2019]%
	\textbf{Software Engineering Ph.D Intern}\, Google, Sunnyvale, CA.
	\par Helped develop a domain-specific language for modeling constraints in data center planning.
	Added support for data defined as protocol buffer messages.
%
\entry*[2018]%
	\textbf{Software Engineering Ph.D Intern}\, Google, Sunnyvale, CA.
	\par Implemented a tool for cleaning build dependencies in System Verilog projects.
%
\entry*[2017]%
	\textbf{Software Engineering Ph.D Intern}\, Orbital ATK, Plymouth, MN.
	\par Embedded development utilizing C and Quantum Platform.
	Built a graphical Python tool for testing \& debugging communications between avionics components.
	%Implemented message encoding and decoding for communication with third-party hardware.
%
\end{rubric}