\begin{rubric}{Miscellaneous Experience}

\entry*[2019] \textbf{Teaching Assistant}, Advanced Programming Principles with OCaml.
\entry*[2016] \textbf{Teaching Assistant}, Programming Languages.
\entry*[2016 -- 2020] \textbf{Software Lead}, LPRD Rocketry, a student group building and testing liquid-propellant rocket engines.
\entry*[2013 -- 2015] \textbf{Undergraduate Researcher}, Minnesota Space Grant Stratospheric Ballooning Team.
\entry*[2011 -- 2015] \textbf{Member}, University of Minnesota Solar Vehicle Project.
\entry*[2012] \textbf{Undergraduate Researcher}, David Odde biophysics laboratory group, studying microtubule dynamics in human glioma cells.
\entry*[2022 -- 2023] \textbf{Leader}, St. Lawrence Catholic Young Adult Group.

\subrubric{Personal Projects}
\entry*[2022] \textbf{Hardware chess}, a complete implementation of a chess AI engine on an FPGA, in Bluespec.
\url{https://github.com/krame505/hardware-chess}
\entry*[2020] \textbf{\href{https://carbles.net}{carbles.net}}, a web version of the multiplayer card game Carbles, featuring an AI player using Monte-Carlo Tree Search.
\url{https://github.com/krame505/carbles-ai}
\entry*[2020] \textbf{Feline telepresence robot}, a robot designed remotely monitor, feed and entertain cats.
\url{https://github.com/krame505/feline-telepresence-robot}


\subrubric{Awards and Achievements}
\entry*[2024 -- 2025] \textbf{Doctoral Dissertation Fellowship}, University of Minnesota.
\entry*[2020] \textbf{Distinguished Paper Award}, “Strategic tree rewriting in attribute grammars", SLE 2020.
%
\entry*[2015] \textbf{Graduated college at age 15}, consistently making Dean's List.

\end{rubric}